Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-15 R/model_fcs_markdown.Rmd
Update

```{r message = FALSE, tidy = TRUE}
library(here)
library(tidyverse)
library(ggbeeswarm)
library(patchwork)
library(brms)
library(DHARMa)
library(bayesplot)
library(loo)
library(tidybayes)
library(emmeans)

@@

```{r}
createDHARMa(
  simulatedResponse = t(posterior_predict(m_1)),
  observedResponse = sites$n,
  fittedPredictedResponse = apply(t(posterior_epred(m_1)), 1, mean),
  integerResponse = TRUE
  ) %>%
  plot()
createDHARMa(
  simulatedResponse = t(posterior_predict(m_2)),
  observedResponse = sites$n,
  fittedPredictedResponse = apply(t(posterior_epred(m_2)), 1, mean),
  integerResponse = TRUE
  ) %>%
  plot()
```

@@

```{r}
(emm <- emmeans(m_3, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```

>>>>

```{r message = FALSE, tidy = TRUE}
library(here)
library(tidyverse)
library(ggbeeswarm)
library(patchwork)
library(brms)
library(DHARMa)
library(DHARMa.helpers)
library(bayesplot)
library(loo)
library(tidybayes)
library(emmeans)

@@

```{r}
DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
```

@@

```{r}
(emm <- emmeans(m_2, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```
